gij bent 2

### 2024-12-11 paper/paper.qmd
generally > broadly
Change PDF margins

---
title: "gij bent 2"
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
  - name: Julie Nijs
    email: julie.nijs@kuleuven.be
    orcid: 000-0002-7421-9887
    affiliations:
      - name: KU Leuven
format:
  html:
    toc: true
  docx:
    toc: false
editor: source
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
df-print: kable
abstract: |
  TODO
execute:
  echo: false
---

@@

Our influence metric is based on the priming ratio from @sevenants_elastic_to_appear and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since generally speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.

>>>>

---
title: "gij bent 2"
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
  - name: Julie Nijs
    email: julie.nijs@kuleuven.be
    orcid: 000-0002-7421-9887
    affiliations:
      - name: KU Leuven
format:
  html:
    toc: true
  docx:
    toc: false
  pdf:
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=20mm
      - heightrounded
editor: source
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
#reference-location: margin
csl: chicago-author-date.csl
df-print: kable
abstract: |
  TODO
execute:
  echo: false
---

@@

Our influence metric is based on the priming ratio from @sevenants_elastic_to_appear and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.
